On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 preliminaries.tex
properly introduce proj lemma

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.

>>>>

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which states the condition under which one can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.
